---
title: "Exploratory Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

#load necessary ALL libraries
library("ggplot2")
library("plotly")
library("dplyr")
library("openxlsx")
library(tidyverse)

# load states dataframe into variable `oscar_data`
oscars_data <- read.xlsx("oscars.xlsx")

# source all R files
source('Chart_1.R')
source('Chart_2.R')
source('Chart_3.R')
```

## An Analysis of Diversity and Inclusiveness in the Oscars

### Authors
* Terresa Tran
* Jacqueline Nguyen
* Quinton Pharr
* Connor Chan

### Date
Winter 2022

### Abstract
Our main question is about the representation of different racial, ethnic and gender groups within the Oscars. We are worried about this because of the lack of representation in the film industry, to address this concern we will use the Oscars dataset from 1927 to 2020. This is important because we hope the findings from the data will help to promote a more diverse and inclusive industry.

### Keywords
Film, Media, Awards, Representation, Academy awards dataset (Oscars)

### Introduction
For this project, we are going to be looking at data from the Academy Awards more specifically the Oscars. We are going to be examining things like the year in which the film was released, and the year in which the movie was nominated. The Oscar ceremony number, along with the category, gender of the nominee or winner, name of the nominee or winner, and racial profile (ethnicity) of the nominee or winner. Lastly, we are going to be looking at the name of the nominated film and the winners where the data will say true for winners, and false for nominations only.
For research questions, we are going to be drawing from the inspiration section of the dataset as well as some of our own, including but not limited to 1. Does the representation of different racial groups in the Oscars reflect the racial diversity of the film industry? 2. What was the reason for the Academy to introduce new diversity rules and why were they necessary? 3. Is there an equal representation of men and women in the entertainment industry? 4. Has the representation of different ethnic groups improved over the years, as reflected by the data? 5. What are the most common categories in which films are nominated and awarded at the Oscars? These are the main things we are going to be examining, but we might also make other discoveries along the way. 

### Related Work
Our research is focused on representation in media but more specifically Hollywood and Academy level environments. Film and Media are vastly produced, shared, and honored and tracing the previous Oscar nominees and winners can help us understand trends in who has been given the opportunities to make impacts on society. One related work we are finding inspiration from is an analysis of the overrepresentation of white actors in Hollywood by Svaikovsky, V., et. al in a published study called [Racial Lines](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/KERZQY). This study analyzed representation by means of tracking dialogue in 780 different Hollywood films between 1970 to 2014, comparing the dialogue distribution between characters/actors of varying ethnicities. It was concluded that there is a privileged “narrative and casting of white folks” and that as such, “it limits the number of visible and audible minorities in these films.

In a study titled [Top 1000 Highest Grossing Movies](https://www.kaggle.com/datasets/sanjeetsinghnaik/top-1000-highest-grossing-movies) similar topics relating to film are covered through categories including sales, genre, runtime, etc. The comparison between these categories allows for a wide variety of representation. With 1,000 movies and 9 internal categorizations, the data represented is vast and relates to the Oscar dataset we chose to study. In addition, the movie data provides concrete values collected from trusted sources including IMDB and Rotten Tomatoes.

In an article by [Rochester Institute of Technology,](https://www.google.com/url?q=https://reporter.rit.edu/views/there-enough-inclusivity-and-representation-hollywood&sa=D&source=docs&ust=1675316943077850&usg=AOvVaw2hunmjGybppl7GgOeF6HOD) their big question was “Is there enough representation in film?” They go on a deep dive about not only racial/ethnic representation, but also about gender and disability as well. Many top rated films that were ranked highly by audience members were often left out of nominations and out of the Academy Awards altogether. 

#### References

Anjali Shiyamsaran | published Nov. 6th, 2019. (n.d.). Is there enough inclusivity and representation in Hollywood? Reporter. Retrieved February 1, 2023, from https://reporter.rit.edu/views/there-enough-inclusivity-and-representation-hollywood 

Naik, S. S. (2022, January 15). Top 1000 highest grossing movies. Kaggle. Retrieved February 1, 2023, from https://www.kaggle.com/datasets/sanjeetsinghnaik/top-1000-highest-grossing-movies 

Svaikovsky, V., Meisner, A., Kraicer, E., &amp; Sims, M. (2018, July 10). Racial Lines. Harvard Dataverse. Retrieved February 1, 2023, from https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi%3A10.7910%2FDVN%2FKERZQY 

### The Dataset
#### Where did you find the data? Please include a link to the data source  
https://www.kaggle.com/datasets/dharmikdonga/academy-awards-dataset-oscars?resource=download

#### Who collected the data?  
The original author is Dharmik Donga, but in the description, it was stated that “I found a basic dataset from Kaggle, but it did not have gender and race of the nominations and winners.” so Dharkmik either drew inspiration from another data set and added gender and race or completely started from the top. Dharkmik also gives an acknowledgment to Raphael Fontes, who is the source for the basic dataset.

#### How was the data collected or generated?  
The data was collected by The Academy Awards database.

#### Why was the data collected?  
The data was collected to look at the racial and gender diversity at the Oscars, and also as a way to track data about the Oscars in a more pleasing way.

#### How many observations (rows) are in your data?  
There are 10.4k rows


How many features (columns) are in the data?  
There are 9 columns/features.


What, if any, ethical questions or questions of power do you need to consider when working with this data?

### Implications
We think some of the possible implications could include things like getting a better understanding of the representation (or more likely a lack of representation) of different racial and ethnic groups in the Oscars. This data/discovery could help with the development of a more inclusive and diverse film industry. Also getting a better understanding of the reasons behind the Academy's diversity rules and the necessity of such rules could help with the development of policies aimed at promoting diversity and inclusiveness in the film industry. This could then lead to the creation of more equitable opportunities and a more representative entertainment industry. We think this would also lead to more diverse casting and probably more perspectives in films and on tv all around. As seen in the data, the film industry has been dominated by old white males and that leads to a very narrow view of the world through film. 

### Limitations & Challenges
The main thing we think we need to consider is the possible limited data availability: The dataset only covers the nominations and winners from 1927 to 2020 and could be considered not as complete as there is no information available past 2020. We think there could also be some biases in the Academy's voting process: The Academy's voting decides the nominations and winners, and might not be representative of the wider population. While this is what we are measuring they might(and probably do) have their own biases and preferences. 
	We think there could also be some discrepancies within how the categories are recorded. As far as we can tell the only things recorded in this dataset are for cinematography, writing, best picture, best actress/supporting actress, and best actor/supporting actor. So the data is missing all of the other very important categories that come into play when making a movie. We also wonder how measuring/voting on these categories/nominees has changed over time. We assume the process in 1927 was much different than the process in 2020 and probably even again in 2023. We think we potentially miss out on some important information when we don't understand how nominees are chosen and what the criteria are. Personally, we think this whole system would make a lot more sense if everything was audience voted but we guess that takes the “critic” part out of it. 


### Summary Information

Write a summary paragraph of findings that includes the 5 values calculated from your summary information R script

### Table

Include a table of aggregate information

Describe why you included the table and what information it reveals

### Chart 1

Describe why you chose this chart and what information it reveals 4-6 sentences

Here's an example of how to run an R script inside an RMarkdown file:

```{r, echo = FALSE, message = FALSE, code = readLines("Chart_1.R")}
chart_1
```

### Chart 2

Describe why you chose this chart and what information it reveals - 4-6 sentences
```{r, echo = FALSE, message = FALSE, code = readLines("Chart_2.R")}
chart_2
```

### Chart 3

Describe why you chose this chart and what information it reveals 4-6 sentences
```{r, echo = FALSE, message = FALSE, code = readLines("Chart_3.R")}
chart_3
```
